
Stallman maintains that a free society can only come about through the adoption of free software, stating that he launched the GNU operating system for the express purpose of freedom and not for technical innovation \citeyear[para. 48]{rms2011}.  Stallman criticizes those who associate the free software movement with the ilk of Linus Torvalds and others who would seek to shift the focus of the free software movement away from ethics and towards practicality. However, if Stallman truly wishes to see widespread adoption of free software, then it would behoove him to also encourage others to capitalize on the practical benefits that made Linux and other open source software solutions so successful.
	
While the transparency of source code serves to inhibit the existence of unethical and malicious code, it also serves to enhance the collaborative nature of software development. A key feature of open source is that it creates an environment in which users mutually borrow and contribute back to one another's projects. The community that formed around the development of Linux embodies this idea very closely. Jim Zemlin, the executive director of the Linux Foundation, provides an illustration in which changes made to Linux to conserve power on a cellphone can be used to benefit supercomputers that also run Linux \citeyear[11:34]{zemlin}. Similarly, the increased availability of code allows developers to adapt software to new challenges. By inheriting httpd's Common Gateway Interface standard, the development of the Apache web server was expedited, as it's creators no longer had the need to build these components from scratch \cite[p.7]{bisson}. 
	
The overall restrictiveness of proprietary software presents a large disadvantage to its users.  Because software is built from source code, the support for any piece of software is ultimately tied to the ability to edit and view that source code. Having access to a product's source code decreases dependency on that product, which is critical should that product become discontinued or should its vendor declare bankruptcy.  Thus, vendor lock-in threatens software users with eventual obsolescence, even in cases where it was possible to retroactively obtain the rights to proprietary code . In one such case involving the migration to new electronic voting machines in New York, the code obtained to make these machines function was licensed for testing and not for deployment \cite[p. 916]{colannino}. Moreover, this issue could have been avoided had the code been released with a free software license, such as the GNU public license. Open source licenses protect the continuous improvements made on software that prevent vendor lock-in \cite[p. 919]{colannino}.

Open source software also has a unique quality assurance mechanism in the form of its peer-review process. The communities that develop around open source software are comprised of passionate individuals who are devoted to problem solving \cite[p. 19]{bisson}. These users endlessly patch vulnerabilities and provide new features. In 2013, it was determined that 6,782 lines of code are added and subtracted to Linux on a daily basis (Zemlin, 2013, 12:03). Consequently, the  constant revision of Linux ensures it's stability and relevance. Yet, the process of open source peer-review is not as straightforward as some would believe. In a study analyzing the bug reports for Mozilla Firefox, Carrol et. al. reevaluates “Linus's Law,” or the idea that “given enough eyeballs, all bugs are shallow”\cite[p. 52]{wang}.  They determine that Mozilla's peer-review process lacked a central focus due to the differing levels skill levels of bug reporters, as disputes commonly arose over the relative importance of certain bugs \citeyear[p. 52]{wang}. However, Carrol et. al.  claim that the careful labeling of duplicate bug reports would solve this problem \citeyear[p. 52]{wang}. 

Due to the ease and availability of open source software, it is very easy to match a software need with an open source solution. When developing Facebook, Mark Zuckerberg used Linux and other free software to build the word's most successful social media platform \cite[6:18]{zemlin}. It can even be argued that a software need—not an ethical need—provided Stallman with the impetus to launch the free software movement. Stallman's animosity towards proprietary software originated from a printer's software's lack of extensibility. When denied permission to add features to the software's source, Stallman vowed that he would never let a programmer share in his frustration \citeyear[para. 19]{rms2015}.  
	
	
	
	
