In a talk given to university students in Paris, Richard Stallman warns of
being a prisoner of the digital world. It does not seem likely that Stallman, a
computer scientist, would preach against a digital lifestyle.  However,
Stallman takes issue not with computers and software on their own, but rather
with software and services that disrespect their users' freedom.  He believes
proprietary software allows companies to insert malicious code that can spy on
users. Companies that make this kind of software, he says, not only deny users
freedom of privacy, but also establish control over those users by keeping
their source code secret. To combat this loss of control, Stallman argues “we
have to extract people from digital society if it doesn't respect their freedom
or we have to make it respect their freedom” (2011, para. 2).

Early in the talk, Stallman clarifies what he means by free software: software
that respects users' freedom. Non-free software, he says, has potential to
control its users. As an example, he points to computers running Microsoft
Windows. Those machines do not respect users' freedom, he says, because they
track "data about the use of the computer" (2011, para.  4). Stallman adds that
malicious software need not be on users' hardware; an online service can also
spy on its users and control users' data . He points out a privacy double
standard—companies do not protect users' privacy, but in the case of DRM, take
great lengths to protect their own.

Stallman chiefly supports his argument for “digital extraction” with an
analysis of what he believes to be the main threats to digital freedom:
surveillance, censorship, restricted data formats, proprietary software,
Internet services, and computer voting. While Stallman alludes to the more
political topics of surveillance, censorship by governments and computer
voting, he devotes much of his talk to the regulation and distribution of
digital media and software.  Stallman envisions a world where users distribute
content easily and freely; accordingly, he views any copy protection measures,
such as the DMCA, as a form of censorship (2011, para.  96). Stallman
encourages his audience to fight the “digital handcuffs” imposed by copy
protection that seek to control how they use content (2011, para. 98).
Stallman similarly opposes proprietary software. Stallman supports his claim
for prohibiting proprietary software by citing its negative effects on
education. He further argues society as a whole would benefit by severing
its dependence on proprietary software (2011, para.  53). To realize his
vision of a world with predominantly free software, Stallman launched the
GNU Project and the Free Software movement.

Stallman supports his arguments with examples carefully tailored to his
audience. Because he delivered his talk at a French university, Stallman
illustrates threats to digital freedom using examples from France and greater
Europe. For instance, he mentions the tracking of bicycles in Paris to
demonstrate threats posed by digital surveillance (2011, para. 8), and he
mentions secret file formats employed by Italian public television to
demonstrate threats posed by restricted data formats (2011, para. 30).
Stallman also enhances his credibility through his use of French terms.
Stallman's explanation of the meaning of “free”—or rather “libre”—software
compliments the subtleties of French (2011, para. 34). Stallman's extensive
explanation of free software also lays an important foundation for the rest of
his talk that can be understood by different audiences.

One should note that Stallman presents his views in a purely ethical context.
In fact, Stallman believes one should only mention free software as “an ethical
issue.” (2011, para. 63). Stallman claims additionally that those who coined
the term “open source” did so to avoid discussing the ethics of free software
(2011, para. 52). Stallman, claiming that the economics of open source software
does not matter, refuses to entertain any argument about it (2011, para. 34).

When talking about a digital society, Stallman draws his ethical truths about a
digital society from a non-digital society. For example, in his section
entitled “the war on sharing,” Stallman, who views book lending as an
“important social act,” criticizes the Amazon kindle for its inability to lend
books (2011, para 98). Stallman maintains that residents of a digital society
must fight to maintain the basic freedoms and rights enjoyed by the non-digital
society of the past.
